\documentclass[11pt, a4paper]{article}
\title{Risk Assessment for Stochastic Dynamics of Cancer Evolution MPhys Project}
\usepackage{geometry}
\geometry{margin = 3cm}
\date{}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{latexsym}

\begin{document}
\section*{Risk Assessment for Stochastic Dynamics of Cancer \\ Evolution MPhys Project}


This project consists of building computer simulations to model the dynamics of cancer. Therefore, the majority of work will be done using a University computer or personal laptop. The work will be carried out in the Schuster Laboratory and the students homes. 


\subsection*{Hazards}

We have identified the following as our main hazards. 

\begin{enumerate}
\item Repetitive strain injury (RSI) from using keyboard and mouse. 
\item Display screen equipment causing eyestrain after prolonged use.
\item Fire risk from the electrical charging equipment of our laptops. 
\item Electrical equipment. 
\item Obstructions providing a trip/fall risk.
\end{enumerate}

\subsection*{Potential Victims}

Items 1 and 2 concern both partners working on the project, without posing any risk to other people. However, items 3, 4 and 5 are a public hazard effecting not only the partners but surrounding people in the Schuster Laboratory.  

\subsection*{Risk Evaluation}

All the above risks are insignificant and can be adequately controlled by following both the University guidelines and ensuring that the current safety guidelines are followed. 

\subsection*{Actions to be taken}

Both persons working on the project need to ensure that this risk assessment is read and ensure that they follow the University guidelines. 

\subsection*{Review}

This risk assessment will be revised if there is change to the project brief. 

\subsection*{Record}

This risk assessment was carried out on 23/09/14 by Dean Markwick and Matthew de Angelis.  

\pagenumbering{gobble}

\end{document}